---
title: "p8105_hw1_hc3563"
author: "Hanchuan Chen"
date: "2024-09-16"
output: github_document
---
```{r message=FALSE}
library(tidyverse)
```

### Problem 1
First, we need to download the plamerpenguins data set and load it.
```{r penguins}
data("penguins", package = "palmerpenguins")
```
Then, let's take a look at this data set. First, we want to know what the data look like. First we will check all of the variable names in this data set:`r names(penguins)`. We also want to see the first row of record:`r head(penguins, n=1)`.

For the size of data set, there are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

We also want to know the mean of flipper length, which is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`, and here is the scatterplot of flipper length and bill length:

```{r echo=FALSE, warning=FALSE}
#create a scatterplot
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()
#save the plot
ggsave("scatterplot.png")
```













