---
title: "p8105_hw1_hc3563"
author: "Hanchuan Chen"
date: "2024-09-16"
output: github_document
---
```{r message=FALSE}
library(tidyverse)
```

### Problem 1
First, we need to download the plamerpenguins data set and load it.
```{r penguins}
data("penguins", package = "palmerpenguins")
```
Then, let's take a look at this data set. First, we want to know what the data look like. First we will check all of the variable names in this data set:`r names(penguins)`. We also want to see the first row of record:`r head(penguins, n=1)`.

For the size of data set, there are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

We also want to know the mean of flipper length, which is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`, and here is the scatterplot of flipper length and bill length:

```{r echo=FALSE, warning=FALSE}
#create a scatterplot
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()
#save the plot
ggsave("scatterplot.png")
```

### Problem 2
Now we will create a dataframe that contains:

* random sample of size 10 from a standard Normal distribution

* a logical vector indicating whether elements of the sample are greater than 0

* a character vector of length 10

* a factor vector of length 10, with 3 different factor “levels”
```{r dataframe}
set.seed(42)
df = tibble(
  vec_num = rnorm(10, sd=1),
  vec_logic = vec_num > 0,
  vec_char = c("My", "name", 'is', 'Hanchuan', 'Chen', 'and', 'my', 'UNI', 'is', 'hc3563'),
  vec_factor = c('high','low','low','medium','medium','low','high','medium','low','high')
)

show(df)
```
And the mean for numeric variable is `r mean(df %>% pull(vec_num))`; mean for logical variable is `r mean(df %>% pull(vec_logic))`; mean for character variable is `r mean(df %>% pull(vec_char))`; and the mean for factor variable is `r mean(df %>% pull(vec_factor))`. As a result, numeric and logical variables can calculate the mean while character and factor variables cannot.

Next, I am going to write a code chunk that converting variable type.
```{r convert_num, eval=FALSE}
logic_to_num = as.numeric(df$vec_logic)
print(logic_to_num)

char_to_num = as.numeric(df$vec_char)
print(char_to_num)

factor_to_num = as.numeric(df$vec_factor)
print(factor_to_num)
```
From the result, we will see that logical variable can be converted to numeric type, while character and factor variables cannot be converted to numeric type. That is because logical values are inherently represented that TRUE = 1 and FALSE = 0. However, convert strings and factors to numeric seems not make sense so they will return NA instead. As a result, when calculating mean for each variables, only numeric and logical variables can be calculated while other two variables cannot.













